Reproducibility of COVID-19 research papers on medRxiv

### 2021-02-16 outputs/paper/paper.Rmd
Add more plots, messy updates to plot script and paper

# Sample Summaries
```{r summary-table}
# open data/open code count summary table
med_open_data_results <- read_csv(here("outputs/data/med_open_data_results.csv"))
med_open_data_results %>% 
                    count(is_open_data, is_open_code) %>%
                    kable(col.names = c("Contains Open Data Markers", "Contains Open Code Markers", "Count"))
```

```{r open-data-published-summary}
med_open_data_results %>% 
  group_by(published) %>% count(is_open_data) %>% 
  pivot_wider(names_from = is_open_data, values_from = n) %>%
  rename("Open Data Markers" = `TRUE`, "No Open Data Markers" = `FALSE`) %>%
  kable()
```

@@

```{r monthly-papers-total}
include_graphics(here("outputs/figures/papers_posted_total.pdf"))
```

```{r monthly-papers-sample}
include_graphics(here("outputs/figures/papers_posted_sample.pdf"))
```

```{r}
include_graphics(here("outputs/figures/prop_open_per_month.pdf"))
```

@@

## First discussion point - Time
- How has open data/code shifted over the course of the pandemic?
- How has open data/code changed with publication rate?

@@

## Third discussion point - Type of Paper
- A significantly higher proportion if

@@

- No open data/code was verified manually, all dependent on algorithm
- Publication info has high rate of false negatives (i.e. medRxiv data seems to miss a lot of papers that go on to be published)
- Want to look at geographic distribution and prevalence of open data/code - influence on open data policies and timing throughout pandemic

>>>>

# Sample Summaries
```{r summary-table}
# open data/open code count summary table
med_open_data_results <- read_csv(here("outputs/data/med_open_data_results.csv"))
med_open_data_results %>% 
                    count(is_open_data, is_open_code) %>%
                    mutate(prop_total = n/1200) %>%
                    kable(col.names = c("Contains Open Data Markers", "Contains Open Code Markers", "Count", "Porportion of Total"))
```

```{r open-data-published-summary}
med_open_data_results %>% 
  group_by(published) %>% count(is_open_data) %>% 
  pivot_wider(names_from = is_open_data, values_from = n) %>%
  rename("Open Data Markers" = `1`, "No Open Data Markers" = `0`) %>%
  kable()
```

@@

```{r monthly-papers-total}
# Number of COVID-related papers posted each month in total
include_graphics(here("outputs/figures/papers_posted_total.pdf"))
```

```{r monthly-papers-by-condition}
# Number of papers posted each month from the sample
# include_graphics(here("outputs/figures/papers_posted_sample.pdf"))
# Likely don't need this anymore, see monthly-papers-sample-2
```

```{r proportion-of-open-data}
# Proportion of papers posted with open data or open code each month
include_graphics(here("outputs/figures/prop_open_per_month.pdf"))
```

```{r monthly-papers-by-condition}
# Number of papers for each open data/code status per month
include_graphics(here("outputs/figures/stack_conditions_plot.pdf"))
```
- Proportion of open data/code has fluctuated over time but shows no consistent overall increase or decrease over the course of the pandemic
- Proportion of open data seems to be relatively unimpacted by the number of papers posted to medRxiv in any given month
- Open code dipped in summer months when posting rate to medRxiv was high, bit questionable
- Open code follows similar patterns of increase/decrease as data but ultimately is less prevelant in the repository

# Publication
```{r}
med_open_data_results %>% 
  group_by(published) %>% count(is_open_data) %>% 
  pivot_wider(names_from = is_open_data, values_from = n) %>%
  rename("Open Data Markers" = `1`, "No Data Code Markers" = `0`) %>% kable()
```

```{r}
med_open_data_results %>% 
  group_by(published) %>% count(is_open_code) %>% 
  pivot_wider(names_from = is_open_code, values_from = n) %>%
  rename("No Open Code Markers" = `0`, "Open Code Markers" = `1`) %>% kable()
```

# Type of Paper
```{r}
# Number of open data/code papers by keyword for different types
include_graphics(here("outputs/figures/paper_type_keywords_plot.pdf"))
```
- Once data is restricted to certain types of papers - those including modeling, simulation, or machine learning - the availability of open data and code becomes much higher than the data set overall
- Relatively small sample size, but still important to note?
- Also an expected result

@@

## Open Data/Code in broader context
- Discussion on open data/code in general and in life/medical sciences
- Are these a good indicator of reproducibility? How much do these contribute to reproducibility?

## First discussion point - Time
- Important to note that time plays a role in geographic focus in this context - early cases/research in China, then east and Southeast Asia, differences in different local data practices/policies
- On one hand good that there did not appear to be a drop in proportion of papers with open data/code as posting rates have risen, but also interesting to note that there has not been an overall increase
-

@@

## Third discussion point - Type of Paper
- Public health modeling/simulation papers more important near beginning of pandemic when less was understood about COVID as a disease specifically
- Perhaps contributed to the fact that the rate of open data/code from beginning of pandemic has been consistent throughout despite what we would hope is an increase in availability of COVID-19-related data?

@@

- No open data/code was verified manually, all dependent on algorithm
- Publication info has high rate of false negatives (i.e. medRxiv data seems to miss a lot of papers that go on to be published)
- Want to look at geographic distribution and prevalence of open data/code - influence on open data policies and timing throughout pandemic
- Extend research to other indicators of reproducibility
